Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-08-01 literature/paper_draft.qmd
move figures in 1st sim to appendix

  Because of this structure, the VAR(1) coefficients matrix would have entries between groups being zeros. To save space, we will only illustrate the settings of the second structure (6 groups of 6) in @fig-settings-6x6, and the first and third structure is similar.

@@

>>>>

Because of this structure, the VAR(1) coefficients matrix would have entries between groups being zeros. To save space, we will only illustrate the settings of the second structure (6 groups of 6) in @fig-settings-6x6, and the illustrations of the first and third structure is attached in @sec-sim-supplement Appendix.

@@

## Simulation Settings: Supplementary Figures {#sec-sim-supplement}
